The problem and promise of scale in multilayer animal social networks

### 2020-02-14 paper/manuscript.Rmd
add conclusion para todos

Multilayer networks remain a nascent but powerful tool in animal behavioural
ecology. We demonstrate the potential novel analyses that vary social, spatial,
and temporal scale within a multilayer framework. In our caribou case study, we
show that (1) multilayer social networks can be, but are not always,
scale-dependent, and (2) the use of multilayer networks could be useful for
identifying habitat or season-specific social processes. Our analyses of social,
spatial, and temporal scales in multilayer network framework highlight potential
to identify scales at which different properties of layers within a multilayer
network show the most variability. Furthermore, we discuss the potential
integration of individual phenotypes and fitness, collective movement, and
habitat selection for future analyses considering spatial ecology using
multilayer networks.

<!-- Alec, I think you need to include a paragraph reflecting on the importance of scale and ~3 critical things we should take away from this (maybe especially in light of including spatial data?) -->

>>>>

Multilayer networks remain a nascent but powerful tool in animal behavioural
ecology. We demonstrate the potential novel analyses that vary social, spatial,
and temporal scale within a multilayer framework. In our caribou case study, we
show that (1) multilayer social networks can be, but are not always,
scale-dependent, and (2) the use of multilayer networks could be useful for
identifying habitat or season-specific social processes. Our analyses of social,
spatial, and temporal scales in a multilayer network framework highlight the potential
to identify scales at which different properties of layers within a multilayer
network show the most variability. Furthermore, we discuss the potential
integration of individual phenotypes and fitness, collective movement, and
habitat selection for future analyses considering spatial ecology using
multilayer networks.

<!-- 
TODO: Schneider 2001, Levin og,

Alec, I think you need to include a paragraph reflecting on the importance of scale and ~3 critical things we should take away from this (maybe especially in light of including spatial data?) -->
